Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-03-14 paper.tex
Rewritten and revised Intro and SoA
They have to be rewritten completely. The SoA is the usual this guys do this, some other guys do that. We should present an argument for our paper, along the lines of

* Prediction is usually based on time series forecasting (refs) or, in some cases, in x or y from blogs (refs).
* however, predicting the reaction to new products is hard for two reasons: no historial data (refs) and difficult processing of available variables: categorical, non-relevant, whatever (refs).
* Even so, these guys (refs) have managed to do this and that, but they are black box (ref

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is launched the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper, we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached the shelves. 
Several years 
% Antonio - Decir cuántos años son, que no me acuerdo.
of data on published books in Spain have been processed by means of data visualisation and other feature selection techniques. The aim is to find out what are the variables that have more impact on sales, and then use machine learning and forecasting methods to predict sales, and, from them, estimate the print-run.
The described methodology improves the forecasting running time and is eventually able to predict sales with remarkable accuracy. Moreover, the proposed method has been validated by the company that provided the data and incorporated in a business intelligence tool for publishers,
since the obtained models provide a reliable guidance on the decision process of
publishing a book, without human intervention 
either for the operation or for interpretation.
% Antonio - esto es cierto??? :D
\end{abstract}

@@

Publishing a book, as releasing any other product, implies several
types of risks and costs due to
the complexity and derived expenses of the production and distribution processes. 
% tienes que enmarcar el problema. Se trata de productos culturales
% con soporte físico y con ventas relativamente pequeñas. Libros,
% discos, no sé si alguna cosa más. - JJ
A newly launched product could be, additionally, completely new to the company (not a new version or edition of a previous product), and sales forecasts can
only be based on the experience of other similar products. 
In this scope, having accurate estimations of future sales of the new
product is extremely important \cite{ChingChin2010}, so that production
runs do not exceed predicted sales. 
Indeed, several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancing in the 
%FERGU: an enhancing está bien dicho? Mejor "an enhacement", no?
production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.

@@

Book publishers, as well as other content producers, release new {\em
  products} more frequently than other industries, so that they face the
problem of predicting sales quite often. The issue, in this case, is to print an
adequate number of copies but not too many, as the unsold volumes will
lead to losses and sunk inventory cost, 
% Antonio - 'sunk inventory cost' es corecto?
whereas if the number of printed copies was not enough, you can always print more. 
%FERGU: el you ese es muy coloquial, reescribir
% Antonio - Esto habría que matizarlo más, de hecho, decirlo va un poco en contra de nuestro artículo, ya que simplifica el problema. Yo indicaría que errores en predicciones por exceso o por defecto tienen MUCHAS pegas (ambos casos), si bien el exceso es peor, claro, pero decir que lo otro es también muy negativo y por eso hay que ajustar muy bien la predicción. ;)
% Se podría señalar, por ejemplo:
% - repetición de costes de distribución
% - mala impresión al cliente/lector, que pueden repercutir negativamente en las ventas
% - algunas más... :D
In this sense, errors in one or the other direction do not have the same impact, although a temporal scarcity of a book that is selling well is also a problem.
% Antonio - esto habría que rescribirlo de acuerdo a lo anterior que comento. ;)
%FERGU: lo de one or the other direction creo que confunde

Thus, it is extremely important to develop an accurate predictive tool which could accurately forecast the future sales a new book will achieve, in order to optimise production and to improve the publishing company profits or minimise losses \cite{Zhao2001}. This is the main objective of this paper.
%FERGU: entonces el objetivo es desarrollar una herramienta? La metodología? Dejarlo más claro en todos los sitios
An example is the optimisation of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. 
% Antonio - podrías extender un poco el ejemplo? Es decir, describir un poco más lo que se hace en ese trabajo. ;)

However, designing such an accurate predictive tool is a difficult task in this scope, as book sales are influenced by several factors that make them fluctuate and, moreover, usually they might be not controllable and even unknown.
%FERGU: "moreover, usually" son dos adverbios juntos y queda un poco raro 
For instance, some are related to decisions on purchases, others with freight 
%FERGU: some factors para dejarlo claro
traffic, or others with the distribution strategy \cite{Little1998}.

Thus, it is very important to know the product and the variables that
might affect the sales, and how an expert manager takes them into account \cite{Armstrong2001,SThomassey2014}. 
                                % ¿Esto también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ
                                % [Pedro] esto iba referido a la Industria Editorial.
Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
%FERGU: some ... variables, no?
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they do? What are the results?

In this research, the problem of how many units should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}},
a company that provides management systems and services for book shops,
% Antonio - 'libraries' o 'book shops'? Supongo que lo segundo. ;D
publishers and distributors. 
Usually, the company's expert sales managers analysed historical data 
and applied their knowledge using external variables to compute correct estimations (predictions), for instance, she can decide increasing or decreasing the sales prediction based on season or sales period.
                        % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.
%In any case, in general companies usually use a forecasting model and then, 
%an expert applies his knowledge, as the company might require an 
%interpretable and understandable model. 
However, carrying out the analysis and forecasting process as a human expert,
may lead to a `fuzzy-like' analysis, which may not take all the variables into account. 
%FERGU: fuzzy-like existe? suena raruno :P
In addition, the process might be tedious, especially when the amount
of data is quite large, and even, different experts can reach different
predictions from the same dataset \cite{ChingChin2010,Sanders1994}.

For these reasons, the industry requires the best suited forecasting
techniques to be adopted so that, estimating sales task is carried out
reliably, accurately, and in an automatic way.

With this issue in mind, in this paper a data visualisation and preprocessing strategy to find out what are the relevant variables describing a book in the prediction of book sales is proposed; then several standard data mining models 
for sales forecasting are evaluated so a publishing company 
can deduce and optimise print-run.
% Antonio - cambiar este párrafo para describirlo como un proceso en dos pasos:
% - análisis y extracción
% - predicción

% Antonio - Además habría que justificar bien (con citas) el por qué de la extracción/selección de características, por ejemplo:
% - menor tiempo de procesamiento
% - mejores resultados (si algunas variables interfieren entre sí)

@@

Sales forecasting is a problem which has been addressed several times in the literature. Most of the studies have been conducted using different analysis and forecasting methods, such as regression models \cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy systems \cite{Mastorocostas2001}, applied to different industrial sectors.
% ¿Y qué? Esta frase
% no aporta nada. La primera frase
% tiene que enmarcar el estado del
% arte - JJ
% Antonio - la he intentado mejorar.

Specifically, Time-Series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
is perhaps the most used technique to tackle the sales forecasting problems. 
The efficiency of these techniques strongly depends on the field of application 
and the correctness of the problem data. However, since they require a large amount of data for predicting sales, these methods are not the most suitable for this task \cite{ChingChin2010}.

This is the case of new book sales forecasting, a problem with issues such as 
dealing with quite limited data (just a few variables are known in advance) or the existence of several categorical values (which are harder to be processed). Given these issues, finding adequate forecasting techniques and selecting 
the best method to use is also a problem \cite{ChingChin2010}.
Moreover, in the case of new unpublished-books, there are no historical data to define patterns, and only some descriptive data about the new book are available 
\cite{ChingChin2010,FaderHardie2005,Madsen2008}. Thus, not any time-series forecasting method can be used \cite{Madsen2008,ChernWSF15}.

For this reason, usually the methods used to predict book sales have been generally based on experts' experience. They analyse data about sales and, taking into account their knowledge in industry, their experience, and their perception about trends, could make decisions on the companies production (how many books should be printed when a new book is published).
%FERGU: quitad los paréntesis :)
This is a complex problem, since the predictions are influenced by external variables that must be taken into account, such as seasonality, promotions or fashions that expert managers might subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}.

  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works have proposed analyzing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon et al. propose using the number of blog references as an indicator of the success of a book, and thus, its sales. Different sales patterns are observed by analysing data obtained.
% Antonio - describir esos 'sales patterns'. ;)
% FERGU: y también cuales son esos 'data obtained'
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied to the problem of unpublished-books sales prediction.
%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?

@@

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data are available, classical time series 
forecasting methods can be applied, which is what the authors do in \cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy neural networks to forecast the future sales of a printed circuit board is proposed.
A similar method is described by Chern et al. \cite{ChernWSF15}, who analyse 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic `word-of-mouth' influences product sales. The proposed method is suitable for those sales forecasting problems with a big amount of online reviews and historical data.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
When a new book is launched the publisher faces the problem of
how many books should be printed for delivery to bookstores. Printing too many is the main issue,
since it implies a loss of investment due to inventory excess. In this
paper, we are tackling the problem of predicting total sales in order to 
print the right amount of books, doing so even before the book has
reached the shelves. 
Several years 
% % Antonio - Decir cuántos años son, que no me acuerdo.
% of data on published books in Spain have been processed by means of
% data visualisation %visualization does not "process". I propose an alternative
%  and other feature selection techniques. 
We have been working on a data set that includes the complete sales
data for books published in Spain across several years. After an
initial exploratory phase using visualization techniques, we have
applied several feature selection techniques in order
to find out what are the variables that have more impact on sales, and
then used machine learning to create a model and forecast sales. 
The described methodology improves the forecasting running time  %with
                                %respect to what?- JJ
and is
eventually able to predict sales with remarkable accuracy. Moreover,
the proposed method was validated by the company that provided
the data and incorporated in a business intelligence tool for
publishers, % We shouldn't say this, it's outside the bounds of the
            % paper. Besides, it was a different technique - JJ
since the obtained models provide a reliable guidance on the decision process of
publishing a book, without human intervention 
either for the operation or for interpretation.
% Antonio - esto es cierto??? :D
% We should simply say: 
% The method presented here provides a reliable data processing
% technique for editorial data and also yields a reasonable result
% that allows publishers to forecast sales and then create the
% appropriate print run without incurring in losses. 
%
% Besides, if this is true:
% It also provides a method that is able to provide insight on the
% decisions that have an influence on the print run for publishers. 
\end{abstract}

@@

Publishing a book, as releasing any other cultural product with a
physical substrate, implies several
types of risks and costs due to
the complexity, and derived expenses, of the production and
distribution processes.  When a company is faced with the problem or
releasing a completely new product, in the sense that it is an unknown
author or a new topic with no track record, sales forecasts can
only be based on the experience obtained from other similar products,
but the definition of ``similar'' itself is obscure and, sometimes,
subjective. Even if it is a known author or topic, having accurate
estimations of future sales of the new 
product is extremely important \cite{ChingChin2010}, so that production
runs do not exceed predicted sales by too much. 
Indeed, several studies have demonstrated that improving sales predictions 
(a reduction of forecasting errors) results in an enhancement in the 
%FERGU: an enhancing está bien dicho? Mejor "an enhacement", no?
production process \cite{Bayraktar2008,Fildes2010,Saeed2008,Zhao2002}.
%which should be obvious from the get go, don't know why you need 4
%papers to affirm that - JJ

@@

The problem is specially acute for book publishers, who, among other
content providers, release new {\em products} more frequently than
other industries, so that they face the 
problem of predicting sales quite often. The issue, in this case, is to print an
adequate number of copies but not too many, as the unsold volumes will
lead to losses and sunk inventory cost, 
% Antonio - 'sunk inventory cost' es corecto?
% Sí, pero corecto no lo es. - JJ
whereas if the number of printed copies was not enough, a new print
run can be made, resulting in temporary losses due to lack of supply;
a real problem, to be sure, but less dire than having too many unsold
books.  
%FERGU: el you ese es muy coloquial, reescribir
% Antonio - Esto habría que matizarlo más, de hecho, decirlo va un poco en contra de nuestro artículo, ya que simplifica el problema. Yo indicaría que errores en predicciones por exceso o por defecto tienen MUCHAS pegas (ambos casos), si bien el exceso es peor, claro, pero decir que lo otro es también muy negativo y por eso hay que ajustar muy bien la predicción. ;)
% Se podría señalar, por ejemplo:
% - repetición de costes de distribución
% - mala impresión al cliente/lector, que pueden repercutir negativamente en las ventas
% - algunas más... :D
% Corregido - JJ
In this sense, errors in one or the other direction do not have the same impact.
% Antonio - esto habría que rescribirlo de acuerdo a lo anterior que comento. ;)
%FERGU: lo de one or the other direction creo que confunde
% Lo que habría que decir es hablar de cómo hemos tratado una u otra
% cosa. ¿Estamos sesgando hacia predecir menos ventas de las que
% habría? ¿O simplemente es por tener un poco de background? Igual
% deberíamos haberlas tratado de forma diferente. - JJ

Thus, it is extremely important to develop an accurate predictive method
which could accurately forecast the future sales a new book will
achieve, in order to optimise production, improve the publishing
company profits or minimise losses \cite{Zhao2001}. This is the main
objective of this paper. 
%FERGU: entonces el objetivo es desarrollar una herramienta? La metodología? Dejarlo más claro en todos los sitios
An example is the optimisation of sales \cite{Mattila2002} by
improving profit margins by selling the whole print-run. 
% Antonio - podrías extender un poco el ejemplo? Es decir, describir
% un poco más lo que se hace en ese trabajo. ;)
% An example of what? Does that go there? - JJ

However, designing such an accurate predictive tool is a difficult
task in this scope, as book sales are influenced by several factors
that make them fluctuate and, moreover, usually they might be not
controllable and even unknown. 
%FERGU: "moreover, usually" son dos adverbios juntos y queda un poco raro 
For instance, some are related to decisions on purchases, others with freight 
%FERGU: some factors para dejarlo claro
traffic, or others with the distribution strategy \cite{Little1998}. % This paragraph is rather useless - JJ

Thus, it is very important to know the product and the variables that
might affect the sales, and how an expert manager takes them into account \cite{Armstrong2001,SThomassey2014}. 
                                % ¿Esto también pasa en la industria de la
                                % moda. ¿Qué vamos a usar de esto? - JJ
                                % [Pedro] esto iba referido a la Industria Editorial.
Their impact is difficult to estimate and it is not constant over time, 
hence the difficulty to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some may have correlations between them. 
%FERGU: some ... variables, no?
However, these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} 
or stepwise regression analysis (SRA) \cite{Chang2009}. % What do they
                                % do? What are the results?
% This is a state of the art? Are we already in the state of the art?
% - JJ

In the research published in this paper, the problem of how many units should be printed 
when a new book is published is faced using data provided by the 
Spanish publishing company Trevenque Editorial S.L.\footnote{{\tt http://editorial.trevenque.es}},
a company that provides management systems and services for bookshops,
% Antonio - 'libraries' o 'book shops'? Supongo que lo segundo. ;D
publishers and distributors. 
Usually, the company's expert sales managers analysed historical data 
and applied their knowledge using external variables to compute
correct estimations (predictions), for instance, she can decide
increasing or decreasing the sales prediction based on season or sales
period.                         % varias citas - JJ
                        % [Pedro] lo modifico para comentar quienes nos facilitaron los datos
                        %  y que así era como funcionaban hasta ese momento.
%In any case, in general companies usually use a forecasting model and then, 
%an expert applies his knowledge, as the company might require an 
%interpretable and understandable model. 
However, carrying out the analysis and forecasting process as a human expert,
may lead to a `fuzzy-like' analysis, which may not take all the variables into account. 
%FERGU: fuzzy-like existe? suena raruno :P
In addition, the process might be tedious, especially when the amount
of data is quite large, and even, different experts can reach different
predictions from the same dataset \cite{ChingChin2010,Sanders1994}.

For these reasons, the industry requires the best suited forecasting
techniques to be adopted so that, estimating sales task is carried out
reliably, accurately, and in an automatic way. % Iterative. Another
                                % useless paragraph - JJ

With this issue in mind, in this paper a data visualisation and
preprocessing strategy to find out what are the relevant variables
describing a book in the prediction of book sales is proposed; then
several standard data mining models  
for sales forecasting are evaluated so a publishing company 
can deduce and optimise print-run.
% Antonio - cambiar este párrafo para describirlo como un proceso en dos pasos:
% - análisis y extracción
% - predicción
After this initial processing phase, we apply machine learning
techniques to create a sales model and use it to predict them.

% Antonio - Además habría que justificar bien (con citas) el por qué de la extracción/selección de características, por ejemplo:
% - menor tiempo de procesamiento
% - mejores resultados (si algunas variables interfieren entre sí)
% - Permiten saber qué variables son las que influyen realmente en el
% resultado. Esto es lo único importante - JJ

@@

Sales forecasting is a problem which has been addressed several times
in the literature. Most of the studies have been conducted using
different analysis and forecasting methods, such as regression models
\cite{Papalexopoulos1990}, neural networks \cite{Yoo1999} or fuzzy
systems \cite{Mastorocostas2001}, applied to different industrial
sectors. 
% ¿Y qué? Esta frase
% no aporta nada. La primera frase
% tiene que enmarcar el estado del
% arte - JJ
% Antonio - la he intentado mejorar.
% Muchas cosas de la intro tendrían que venir aquí, al estado del
% arte. Habría que reescribir la intro. - JJ

Specifically, Time-Series prediction methods \cite{Chu2003,Brown1959,Winters1960,Box1969,Papalexopoulos1990} 
is perhaps the most used technique to tackle the sales forecasting
problems. The efficiency of these techniques strongly depends on the field of application 
and the correctness of the problem data. However, since they require a
large amount of data for predicting sales, these methods are not the
most suitable for this task \cite{ChingChin2010}. And they cannot be
applied before the book is published, as is the objective of this
paper.

In this case, just a few variables are known in advance
\cite{ChingChin2010,FaderHardie2005,Madsen2008}, and some of 
them are categorical, harder to process, even more so if the number
of categories is high. Given these issues, finding adequate
forecasting techniques and selecting  
the best method to use is also a problem \cite{ChingChin2010}. % Qualify this citation - jj

% Thus, not any time-series forecasting method can be used
% \cite{Madsen2008,ChernWSF15}. 
% Qualify those references!!! What do they say?

For this reason, usually the methods used to predict book sales have
been generally based on experts' experience.% Reference - JJ
 They analyse data about
sales and, taking into account their knowledge in industry, their
experience, and their perception about trends, could make decisions on
the companies production (how many books should be printed when a new
book is published). 
%FERGU: quitad los paréntesis :)
% Fergu: quítalos tú, tío, aquí puede editar todo el mundo - JJ
This is a complex problem, since the predictions are influenced by
external variables that must be taken into account, such as
seasonality, promotions or fashions that expert managers might
subjectively apply \cite{Lapide1999,ChingChin2010,ChernWSF15}. % This
                                % has something to do with the
                                % previous paragraph? Put it there!!! 
%
  %[pedro] sobre la industria editorial no hay trabajos sobre predicción de ventas.
  % Lo habitual ha sido usar el conocimiento de expertos para realizar predicciones 
  %  o aconsejar acerca de la cantidad de libros a imprimir.
  % Lo más parecido que he encontrado son dos trabajos (uno en realidad) de Moon et al. 
  %  sobre "Use Blog Information As Book Sales Prediction":
  %     Moon2010ICSSSM
  %     Moon2010ICEC
Recently, some works have proposed analyzing relationships between on-line information 
and book sales \cite{Moon2010ICSSSM,Moon2010ICEC}. Specifically, Moon
et al. propose using the number of blog references as an indicator of
the success of a book, and thus, its sales. Different sales patterns
are observed by analysing data obtained. 
% Antonio - describir esos 'sales patterns'. ;)
% FERGU: y también cuales son esos 'data obtained'
However, the authors used in these papers historical data from published books, 
so their proposed methodology can not be applied to the problem of unpublished-books sales prediction.
%FERGU: pero nosotros también usamos historical data, no? qué diferencia hay con lo nuestro? por qué lo nuestro es lo mejor?

@@

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data are available, classical time series 
forecasting methods can be applied, which is what the authors do in
\cite{Chang2009}, where a hybrid model integrating K-Means and fuzzy
neural networks to forecast the future sales of a printed circuit
board is proposed. % We have been talking above that above and SAID IT
                   % DIDN'T WORK? Why do we say it here again?
A similar method is described by Chern et al. \cite{ChernWSF15}, who analyse 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic `word-of-mouth' influences product sales. The proposed method is suitable for those sales forecasting problems with a big amount of online reviews and historical data.
